On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-08-28 paper.tex
Updated "to do" list

The rest of the paper is organized as follows. Fundamental results are presented in \S\ref{part: fund results}, which form the basis of the subsequent analysis. The direct and inverse problems for a deterministic segment are considered in \S\ref{part: max}, first for real-valued lengths, and then for integer-valued lengths on a unit square grid. The analysis for the random segment is carried out in \S\ref{part: rand}. The average number of tiles is computed in general, and the probability that the segment visits the maximum number of tiles is obtained for a square grid.

@@

\begin{figure}
\centering%
\includegraphics[width=.7\textwidth]{ijLS_1}%
\caption{Relationship of segment length and number of visited tiles with the width and height of the canonical rectangle, for $a=b$
}%
\label{fig: ijLS_1}%
\end{figure}%
% ***Combine this figure and the next into one figure with two subfigures (stacked vertically, size similar to now)? This has been done in others
% ***Are these figures necessary? They were created with the aim of helping understand the first of the two propositions on $\mss$. Now that proposition has been removed. They are probably still useful, but maybe the text about these figures needs to be rewritten.

@@

>>>>

The rest of the paper is organized as follows. Fundamental results are presented in \S\ref{part: fund results}, which form the basis of the subsequent analysis. The direct and inverse problems for a deterministic segment are considered in \S\ref{part: max}, first for arbitrary grids and then for a square grid. The analysis for the random segment is carried out in \S\ref{part: rand}. The average number of tiles is computed for arbitrary grids, and the probability that the segment visits the maximum number of tiles is obtained for a square grid.

@@

\begin{figure}
\centering%
\includegraphics[width=.7\textwidth]{ijLS_1}%
\caption{Relationship of segment length and number of visited tiles with the width and height of the canonical rectangle, for $a=b$
}%
\label{fig: ijLS_1}%
\end{figure}%
% ***Maybe combine this figure and the next into one figure with two subfigures (stacked vertically, size similar to now). Not sure. It has been done in others
% ***Are these figures necessary? They were created with the aim of helping understand the first of the two propositions on $\mss$. Now that proposition has been removed. They are probably still useful, but maybe the text about these figures needs to be rewritten.

@@

***Comment about how the new formula has two terms with definite meanings: The first term is the distance-squared to the closest point on the diagonal, The second term is additional distance-squared incurred from rounding (i,j) to integers
